DeepAutoTrack (DAT): Vehicle Trajectory Prediction for Autonomous Driving

### 2018-01-26 paper/cvpr2018/cvpr2018_3790.tex
update

Vision-based deep neural networks are crucial components for autonomous driving in terms of visual understanding and decision making.
These models need to be temporally consistent and visually interpretable.
Most recent works focus on using static images for understanding visual semantics, ignoring the temporal consistency of driving conditions; or adopt end-to-end architectures for learning the pilot networks, providing limited interpretability.
In this paper, we raise the question of ``can we predict other traffic participant's future trajectory given previous egomotion visual input?".
The proposed system stems from the issue of human driver reaction time in the autonomous driving context.
Our dual-staged model firstly applies modern convolutional object detectors for spotting traffic participants (i.e., cars in this paper) and robustly tracks the targets of interest.
Then, a novel SEG-LSTM network is incorporated to fuse the multiple-streams from past frames and then predict targets' future trajectories.
We demonstrate the feasibility of predicting future trajectories of vehicles for assisting mediated perception.
We also show the effectiveness of combining various levels of abstractions(e.g., scene semantics, detection bounding boxes) further boost the prediction accuracy across diverse traffic conditions.
\end{abstract}
%%%%%%%%% BODY TEXT
%%% Andrje Karpathy's blog: http://karpathy.github.io/2016/09/07/phd/
%%% Another great resource on this topic is Tips for Writing Technical Papers from Jennifer Widom.
%%% https://cs.stanford.edu/people/widom/paper-writing.html
\section{Introduction}
\begin{figure}[t]
        \centering
        \includegraphics[width=0.45\textwidth]{figures/pull_figure.pdf}
        \caption{ \small{
        We propose a system to predict future trajectories of vehicles. Given historical information, obtained by detection, tracking and semantic segmentation, a multi-stream recurrent neural network is trained to generate future trajectory.}}
        \label{fig:pull_figure}
\end{figure}
%\textbf{\emph{1.1 What is the problem?}}

@@

\begin{figure*}[t]
        \centering
        \includegraphics[width=0.95\textwidth]{figures/framework.pdf}
        \caption{
        \small{The framework for the proposed vehicle future trajectory prediction system. The input is the sequential data (RGB and/or depth maps) up to the current time step obtained from the host car. Target vehicles' sequential bounding boxes are extracted by detection \& tracking module. Along with scene semantics as an auxiliary information, multi-stream inputs are fed into an LSTM to predict future trajectories taking advantages of various levels of abstractions.}
        }
        \label{fig:framework}
\end{figure*}
%\noindent \textbf{RNN for sequence prediction}

@@

We first describe the overall framework for vehicle trajectory prediction and the details of implementation are presented in Sec~\ref{sec:Implementations}.
Our goal is via collecting visual information from the past frames to predict the traffic participants future trajectory. Fig.~\ref{fig:framework} shows the overall architecture of the proposed framework.

@@

\begin{figure}[t]
        \centering
        \includegraphics[width=0.45\textwidth]{figures/SEGLSTM.pdf}
        \caption{
        \small{Diagram of SEG-LSTM model: semantic inputs are one-hot encoded images with channel number $\mathcal{C}$ as the number of semantic categories (we used only ``car" and ``road" as the two semantics used under the context of high-way driving). The higher level semantics are extracted through a four-layer CNN, producing a joint representation of the auxiliary semantic information and the co-ordinate trajectory information.}
        }
        \label{fig:SEGLSTM}
\end{figure}
\subsection{Sequence modeling}

@@

\vspace{\baselineskip}
\noindent \textbf{SEG-LSTM model:}
 takes advantages of scene semantics from  historical frames as auxiliary information $\mathcal{A}$. The second LSTM layer fuses the output from the bottom-most LSTM that encodes co-ordinates embedding with higher level semantic information.
With auxiliary $\mathcal{A}$, the trajectory  $j_{t+1, \ldots, T_F}$  to be predicted can be estimated as:
\begin{equation}
j_{t+1, \ldots, T_F}, \leftarrow  \bm{\mathcal{M}}(j_H, a): \mathcal{J_H} \times \mathcal{A}
\label{eq:SEG-LSTM}
\end{equation}
 Semantic inputs are one-hot encoded images with channel number $\mathcal{C}$ as the number of semantic categories  as in Fig.~\ref{fig:SEGLSTM}. The higher level semantic is extracted through a four-layer CNN, producing a joint representation of the semantic auxiliary information and the co-ordinate trajectory information.
 As described above, the 3D occupancy input  has only six dimensions: $[x, y, w, h, d_{min}, d_{max}]$ encoding the co-ordinates information. So the bottom-most LSTM not only can learn the temporal information between time-varying trajectories,  but also can balance input dimensions of both co-ordinate information and the semantic information.
%Results show that the SEG-LSTM model performs better than the other two temporal model.

@@

\begin{figure*}[t]
        \centering
        \includegraphics[width=0.95\textwidth]{figures/prediction.pdf}
        \caption{
        \small{The prediction results in SYNTHIA dataset. {\color{red}Red: ground truth}; {\color{blue}Blue: SEG-LSTM}; {\color{green}Green: FtS}; {\color{yellow}Yellow: FtF}.
        The results using SEG-LSTM network show that by utilizing the scene semantics (\emph{e.g.}, road, cars), it's able to direct the predicted trajectory from the recurrent net within the most plausible path. Top: SEG-LSTM can help detecting neighboring vehicles and restricts the viable path outside the space occupied by other vehicles. Bottom:  SEG-LSTM confines the possible car trajectories along the space above road.}
                }
        \label{fig:final}
\end{figure*}

>>>>

Vision-based deep neural networks are crucial components for autonomous driving in terms of visual understanding and decision making.
These models need to be temporally consistent and visually interpretable.
Most recent works focus on using static images for understanding visual semantics, ignoring the temporal consistency of driving conditions; or adopt end-to-end architectures for learning the pilot networks, providing limited interpretability.
In this paper, we raise the question of ``can we predict other traffic participant's future trajectory given previous egomotion visual input?".
The proposed system stems from the issue of human driver reaction time in the autonomous driving context.
Our dual-staged model firstly applies modern convolutional object detectors for spotting traffic participants (i.e., cars in this paper) and robustly tracks the targets of interest.
Then, a novel SEG-LSTM network is incorporated to fuse the multiple-streams from past frames and then predict targets' future trajectories.
We demonstrate the feasibility of predicting future trajectories of vehicles for assisting mediated perception.
We also show the effectiveness of combining various levels of abstractions(e.g., scene semantics, detection bounding boxes) further boost the prediction accuracy across diverse traffic conditions.
\end{abstract}
%%%%%%%%% BODY TEXT
%%% Andrje Karpathy's blog: http://karpathy.github.io/2016/09/07/phd/
%%% Another great resource on this topic is Tips for Writing Technical Papers from Jennifer Widom.
%%% https://cs.stanford.edu/people/widom/paper-writing.html
\section{Introduction}
\begin{figure}[t]
        \centering
        \includegraphics[width=0.42\textwidth]{figures/pull_figure.pdf}
        \caption{ \small{
        We propose a system to predict future trajectories of vehicles. Given historical information, obtained by detection, tracking and semantic segmentation, a multi-stream recurrent neural network is trained to generate future trajectory.}}
        \label{fig:pull_figure}
\end{figure}
%\textbf{\emph{1.1 What is the problem?}}

@@

\begin{figure*}[t]
        \centering
        \includegraphics[width=0.90\textwidth]{figures/framework.pdf}
        \caption{
        \small{The framework for the proposed vehicle future trajectory prediction system. The input is the sequential data (RGB and/or depth maps) up to the current time step obtained from the host car. Target vehicles' sequential bounding boxes are extracted by detection \& tracking module. Along with scene semantics as an auxiliary information, multi-stream inputs are fed into an LSTM to predict future trajectories taking advantages of various levels of abstractions.}
        }
        \label{fig:framework}
\end{figure*}
%\noindent \textbf{RNN for sequence prediction}

@@

We first formalized the proposed problem and describe the overall framework as shown in Fig.~\ref{fig:framework}.

@@

\begin{figure}[t]
        \centering
        \includegraphics[width=0.42\textwidth]{figures/SEGLSTM.pdf}
        \caption{
        \small{Diagram of SEG-LSTM model: semantic inputs are one-hot encoded images with channel number $\mathcal{C}$ as the number of semantic categories (we used only ``car" and ``road" as the two semantics used under the context of high-way driving). The higher level semantics are extracted through a four-layer CNN, producing a joint representation of the auxiliary semantic information and the co-ordinate trajectory information.}
        }
        \label{fig:SEGLSTM}
\end{figure}
\subsection{Sequence modeling}

@@

\vspace{\baselineskip}
\noindent \textbf{SEG-LSTM model:}
 takes advantages of scene semantics from  historical frames as auxiliary information $\mathcal{A}$. The second LSTM layer fuses the output from the bottom-most LSTM that encodes co-ordinates embedding with higher level semantic information.
With auxiliary $\mathcal{A}$, the trajectory  $j_{t+1, \ldots, T_F}$  to be predicted can be estimated as:
\begin{equation}
j_{t+1, \ldots, T_F}, \leftarrow  \bm{\mathcal{M}}(j_H, a): \mathcal{J_H} \times convnet(\mathcal{A})
\label{eq:SEG-LSTM}
\end{equation}
 Semantic inputs are one-hot encoded images with channel number $\mathcal{C}$ as the number of semantic categories  as in Fig.~\ref{fig:SEGLSTM}. The higher level semantic is extracted through a four-layer CNN, producing a joint representation of the semantic auxiliary information and the co-ordinate trajectory information.
 As described above, the 3D occupancy input  has only six dimensions: $[x, y, w, h, d_{min}, d_{max}]$ encoding the co-ordinates information. So the bottom-most LSTM not only can learn the temporal information between time-varying trajectories,  but also can balance input dimensions of both co-ordinate information and the semantic information.
%Results show that the SEG-LSTM model performs better than the other two temporal model.

@@

\begin{figure*}[t]
        \centering
        \includegraphics[width=0.95\textwidth]{figures/prediction_2.pdf}
        \caption{
        \small{Visualization of prediction results. Top two rows show the advantage of using semantics in temporal model: {\color{red}Red: ground truth}; {\color{blue}Blue: SEG-LSTM}; {\color{green}Green: FtS}; {\color{yellow}Yellow: FtF}.
        SEG-LSTM can help detecting neighboring vehicles and restricts the viable path outside the space occupied by other vehicles (row 1) and confines the plausible car trajectory along the space above road (row 2).
        Row 3 and 4 show the benefit  of incorporating social factors.
        Row 3 is the visualization for vanilla LSTM. The bottom left car prediction (denoted by red dots) is considered in isolation and could surpass the host car, moving dangerously close to the two front cars. Row 4 is the visualization of social LSTM: by considering two front cars in the scene, the predicted keeps the red dot car in a safer distance from two front cars.
        }
        }
        \label{fig:final}
\end{figure*}
